

\phantomsection
\addcontentsline{toc}{chapter}{REFERENCES}
\begin{thebibliography}{99}

\bibitem{citation-1}Li, Hui, Deliang Yang, Lingling Yang, and Xiaola Lin,\emph{Supervised Massive Data Analysis for Telecommunication Customer Churn Prediction},Big Data and Cloud Computing (BDCloud), Social Computing and Networking (SocialCom), Sustainable Computing and Communications (SustainCom)(BDCloud-SocialCom-SustainCom),pp. 163-169, IEEE, 2016.

\bibitem{citation-2} A. Wangperawong, C. Brun, O. Laudy, and R. Pavasuthipaisit, \emph{Churn analysis using deep convolutional neural networks and autoencoders,},2016,[Online]. Available: https://arxiv.org/abs/1604.05377.
 Accessed: Jan. 25, 2017.
 
\bibitem{citation-3} F. Schwenker and E. Trentin, \emph{“Pattern classification and clustering: A review of partially supervised learning approaches}, ” Pattern Recognition Letters , vol. 37 ,pp. 4–14, Feb. 2014.

 \bibitem{citation-4}
Amezcua, Jonathan, P. Melin, and O. Castillo, \emph{“A Neural Network with a Learning Vector Quantization Algorithm for Multiclass Classification Using a Modular Approachs}, ” Recent Developments and New Direction in Soft-Computing Foundations and Applications, Springer International Publishing,  pp.171–184, 2016.

\bibitem{citation-5}
B. Carlo Migel and P. S, \emph{“Convolutional neural network for vehicle detection in low resolution traffic videos”} in Region 10 Symposium (TENSYMP), 2016 IEEE, IEEE, 2016.
\bibitem{citation-6}
M. F. Møller, \emph{“A scaled conjugate gradient algorithm for fast supervised learning}, Neural Networks, vol. 6, no. 4, pp. 525–533, Jan. 1993.

\bibitem{citation-7}
V. Sowmya, D. Govind and K. Soman, \emph{Significance of incorporating chrominance information for effective color-to-grayscale image conversion},Signal, Image and Video Processing, vol. 11, no. 1, pp. 129–136,
2016.

\bibitem{citation-8}Parth Sane and Ravindra Agrawal, \emph{Pixel Normalization from Numeric Data
	as Input to Neural Networks},IEEE WiSPNET 2017 conference,pp. 2250-2254,2017.

\bibitem{citation-9}J. Deng, W. Dong, R. Socher, L.-J. Li, K. Li, and L. Fei-Fei, \emph{ImageNet: A large-scale hierarchical image database,}, 2009 IEEE Conference on Computer Vision and Pattern Recognition ,2009.
pdf. Accessed: Jan. 25, 2017.

\bibitem{citation-10}MATLAB 2017a, The MathWorks, Natick, 2017.

\bibitem{citation-11}T. MathWorks, “Neural network Toolbox - MATLAB,” in Mathworks.com, 2016. [Online]. Available: https://www.mathworks.com/products/neural-network.html. Accessed: Jan. 25, 2017.

\bibitem{citation-12}Francisco, “Check out this dataset ‘churn in telecom’s dataset’,”
in BigML.com, BigML.com - Machine Learning Made Easy,
2017. [Online]. Available: https://bigml.com/user/francisco/gallery/
dataset/5163ad540c0b5e5b22000383. Accessed: Jan. 25, 2017.
\end{thebibliography}

